Probabilistic Catalogs for Crowded Stellar Fields

### 2013-03-10 paper/ms.tex
commas

In this paper we have developed and demonstrated a Bayesian approach to
making catalogs from astronomical images in the case where the image contains
only stars (or other point sources). The key idea is that instead of computing
a single catalog, the method creates a posterior probability distribution on
the space of possible catalogs that represents our state of knowledge about
the presence and properties of objects in the image. When this is done, the
uncertainties in the imaging are accurately propagated through to scientific
conclusions, for example about the luminosity function of the stars.
This approach was contrasted with the results from the standard \sex~software.
For the bright sources the results were essentially consistent, however the
Bayesian approach was more successful at modelling the distribution of faint
stars. Of course, the Bayesian method is much more computationally intensive,
which is a significant issue in practice.
However, the great value of upcoming imaging data sets, and the irreproducibility of astronomical imaging data in areas of time-domain astrophysics (for example in observations of rare events), make it important to extract as much information as possible from every patch of imaging.  Our view is that the additional CPU time, and the non-triviality of the outputs from our method, will be worth the effort in the next generation of astronomical experiments.
To build a more complete picture of
when our approach is necessary in practice, it will need to be tested against
a wider variety of alternative methods  such as DAOPHOT \citep{1987PASP...99..191S}
and DOLPHOT \citep{dolphot}.

>>>>

In this paper we have developed and demonstrated a Bayesian approach to
making catalogs from astronomical images in the case where the image contains
only stars (or other point sources). The key idea is that instead of computing
a single catalog, the method creates a posterior probability distribution on
the space of possible catalogs that represents our state of knowledge about
the presence and properties of objects in the image. When this is done, the
uncertainties in the imaging are accurately propagated through to scientific
conclusions, for example about the luminosity function of the stars.
This approach was contrasted with the results from the standard \sex~software.
For the bright sources the results were essentially consistent, however the
Bayesian approach was more successful at modelling the distribution of faint
stars. Of course, the Bayesian method is much more computationally intensive,
which is a significant issue in practice.
However, the great value of upcoming imaging data sets and the irreproducibility of astronomical imaging data in areas of time-domain astrophysics (for example in observations of rare events) make it important to extract as much information as possible from every patch of imaging.  Our view is that the additional CPU time and the non-triviality of the outputs from our method will be worth the effort in the next generation of astronomical experiments.
To build a more complete picture of
when our approach is necessary in practice, it will need to be tested against
a wider variety of alternative methods  such as DAOPHOT \citep{1987PASP...99..191S}
and DOLPHOT \citep{dolphot}.
